Methods for Large Scale Learning to Rank

### 2014-02-26 report/BenchmarkResults.tex
nare realisatie mbt google scholar + inleiding pointwise + kritische noot yahoo winners

The challenge overview paper states as one of the lessons of the challenge that the simple baseline \ac{GBDT} model performed very well with a small performance gap to the complex ensemble submissions at the top of the table.

@@

>>>>

The challenge overview paper states as one of the lessons of the challenge that the simple baseline \ac{GBDT} model performed very well with a small performance gap to the complex ensemble submissions at the top of the table.\\

@@

Although the winning \ac{GBDT} models performs very well in terms of \ac{nDCG} their high complexity makes them unsuitable to use in production. The winning models take weeks to train and are very slow during query evaluation.

### 2014-02-26 report/Chapters/Background.tex
nare realisatie mbt google scholar + inleiding pointwise + kritische noot yahoo winners

\chapter{Approaches to Learning-to-Rank}
%TODO: Pointwise, pairwise & listwise beter uitwerken
\section{Pointwise Approach}
Learn from each document in isolation.
Through:
	\begin{enumerate}
	\item regression, when relevance is real-valued
	\item classification, when relevance is categorical
	\item ordinal regression
	\end{enumerate}
\section{Pairwise Approach}
Pointwise approach Learning-to-Rank methods optimise real valued expected relevance, while evaluation metrics like \ac{nDCG} and \ac{ERR} are only impacted by a change in expected relevance when that change impacts a pairwise preference. The pairwise approach solves this drawback of the pointwise approach by regarding ranking as pairwise classification. Aggregating a set of predicted pairwise preferences into the corresponding optimal rank is shown to be a NP-Hard problem. 
\section{Listwise Approach}
Listwise ranking optimises the actual evaluation metric. The learner learns to predict an actual ranking itself without using an intermediate step like in pointwise or pairwise Learning-to-Rank. The main challenge in this approach is that most evaluation metrics are not differentiable. \ac{MAP}, \ac{ERR} and \ac{nDCG} are all discontinuous and non-convex functions, what makes them very hard to optimize.

>>>>

\chapter{Approaches to Learning-to-Rank}
\section{Pointwise Approach}
The pointwise approach can be seen as the most straightforward way of using machine learning for ranking. Pointwise Learning-to-Rank methods directly apply machine learning methods to the ranking problem by observing each document in isolation. They can be subdivided in the following approaches:
	\begin{enumerate}
	\item regression-based, which estimate the relevance of a considered document using a regression model.
	\item classification-based, which classify the relevance category of the document using a classification model.
	\item ordinal regression-based, which classify the relevance category of the document using a classification model in such a way that the order of relevance categories is taken into account. 
	\end{enumerate}
\section{Pairwise Approach}
Pointwise approach Learning-to-Rank methods optimise real valued expected relevance, while evaluation metrics like \ac{nDCG} and \ac{ERR} are only impacted by a change in expected relevance when that change impacts a pairwise preference. The pairwise approach solves this drawback of the pointwise approach by regarding ranking as pairwise classification. Aggregating a set of predicted pairwise preferences into the corresponding optimal rank is shown to be a NP-Hard problem. 
\section{Listwise Approach}
Listwise ranking optimises the actual evaluation metric. The learner learns to predict an actual ranking itself without using an intermediate step like in pointwise or pairwise Learning-to-Rank. The main challenge in this approach is that most evaluation metrics are not differentiable. \ac{MAP}, \ac{ERR} and \ac{nDCG} are all discontinuous and non-convex functions, what makes them very hard to optimize.

### 2014-02-26 report/Chapters/Introduction.tex
nare realisatie mbt google scholar + inleiding pointwise + kritische noot yahoo winners

\chapter{Approach}
A literature study will be performed to get insight in relevant existing techniques for large scale Learning-to-Rank. The literature study will be performed by using the following query:
\begin{itemize}
\item ("learning to rank" OR "learning-to-rank" OR "machine learned ranking") AND ("large scale" OR "parallel" OR "distributed")
\end{itemize}
and the following bibliographic databases:
\begin{itemize}
\item Scopus
\item Web of Science
\end{itemize}

The query incorporates different ways of writing of Learning-to-Rank, with and without hyphens, and the synonymous term \emph{machine learned ranking} to increase search recall, i.e. to make sure that no relevant studies are missed. For the same reason the terms \emph{parallel} and \emph{distributed} are included in the search query. Even though \emph{parallel} and \emph{distributed} are not always synonymous is all definitions, we are interested in both approaches in non-sequential data processing. \emph{large scale} is a term in the search query that is likely to result in a decrease of precision, because this term is also often used in highly efficient sequential approaches. However, the \emph{large scale} term is still included in the query to prevent missing relevant results.\\

>>>>

\chapter{Approach}
A literature study will be performed to get insight in relevant existing techniques for large scale Learning-to-Rank. The literature study will be performed by using the following query:
\begin{itemize}
\item ("learning to rank" OR "learning-to-rank" OR "machine learned ranking") AND ("parallel" OR "distributed")
\end{itemize}
and the following bibliographic databases:
\begin{itemize}
\item Scopus
\item Web of Science
\end{itemize}

The query incorporates different ways of writing of Learning-to-Rank, with and without hyphens, and the synonymous term \emph{machine learned ranking} to increase search recall, i.e. to make sure that no relevant studies are missed. For the same reason the terms \emph{parallel} and \emph{distributed} are included in the search query. Even though \emph{parallel} and \emph{distributed} are not always synonymous is all definitions, we are interested in both approaches in non-sequential data processing.\\

### 2014-02-26 report/RelatedWork.tex
nare realisatie mbt google scholar + inleiding pointwise + kritische noot yahoo winners

The literature research is performed by using the bibliographic databases Scopus and Web of Science with the following search query: \emph{("learning to rank" OR "learning-to-rank" OR "machine learned ranking") AND ("large scale" OR "parallel" OR "distributed")}. An abstract based manual filtering step is applied where I filter those results that actually use the \emph{large scale}, \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}. Studies focusing on efficient query evaluation instead of efficient model training are likely to meet all criteria listed. As a last step I will filter out studies based on the whole document that only focus on efficient query evaluation and not on parallel or distributed learning of ranking functions.

@@

>>>>

The literature research is performed by using the bibliographic databases Scopus and Web of Science with the following search query: \emph{("learning to rank" OR "learning-to-rank" OR "machine learned ranking") AND ("parallel" OR "distributed")}. An abstract based manual filtering step is applied where I filter those results that actually use the \emph{parallel} or \emph{distributed} terms in context to the \emph{learning to rank}, \emph{learning-to-rank} or \emph{machine learned ranking}. Studies focusing on efficient query evaluation instead of efficient model training are likely to meet all criteria listed. As a last step I will filter out studies based on the whole document that only focus on efficient query evaluation and not on parallel or distributed learning of ranking functions.

@@

\subsection{Google Scholar}
The defined search query resulted in 3300 documents.
